null_model

### 2020-10-12 analysis/ts_null_model.Rmd
write out PCA traits

  print(unique(plot_samples$plot_id))
  sample_fd <- as.data.frame(dbFD_joggle(x = trait_mat, a = sample_species_mat, w.abun = TRUE, ...)) %>%
    cbind(plot_samples %>% select(year, plot_id, n))

>>>>

  print(unique(plot_samples$plot_id))
  sample_fd <- as.data.frame(dbFD_mine(x = trait_mat, a = sample_species_mat, w.abun = TRUE, ...)$fd_met) %>%
    cbind(plot_samples %>% select(year, plot_id, n))
